Exploiting the Social Graph: Increasing Engagement via Collaborative Interactive Evolution

### 2017-03-10 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Some Corrections

\author{\IEEEauthorblockN{Mario Garc\'ia-Valdez, Jos\'e Christian Romero, Alejandra Mancilla}
\IEEEauthorblockA{Instituto Tecnol\'ogico de Tijuana\\
Tijuana, Mexico\\
Email: (mario,amherag)@tectijuana.edu.mx,alejandra.mancilla@gmail.com}
\and
\IEEEauthorblockN{Juan Juli\'an Merelo Guerv\'os}
\IEEEauthorblockA{Universidad de Granada, CITIC\\
Email: jmerelo@geneura.ugr.es}
}

@@

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight.
\item Non Graph Gamification (G). Only experience is considered
\item Graph Gamification (GG) . Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window. A screen capture of
this interface is shown in figure \ref{fig:top-users}.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/users_known_1.png}
    \caption{Comparison of two users showing the {\tt knows} relationship.}
    \label{fig:users-graph}
\end{figure}

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/leaderBoard.png}
    \caption{User interface showing top users.}
    \label{fig:top-users}
\end{figure}

@@

The three versions of the EvoDrawing web application were deployed to the
Heroku cloud service with the same configuration: using the
Heroku Free option with a 512 MB of RAM, adding only the GrapheneDB and RedisTOGO plug-ins.
Table \ref{tab:params} shows the parameters used for the evolutionary algorithm. The graph database 
system used in the implementation was Neo4J as it was already available as a plug-in in Heroku, is well documented
and a scalable solution \cite{miller2013graph,holzschuher2013performance}.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.3in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated vs. the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}

>>>>

\author{\IEEEauthorblockN{Mario Garc\'ia-Valdez, Jos\'e Christian Romero Hern\'andez, Alejandra Mancilla}
\IEEEauthorblockA{Instituto Tecnol\'ogico de Tijuana\\
Tijuana, Mexico\\
Email: (mario,amherag)@tectijuana.edu.mx,alejandra.mancilla@gmail.com}
\and
\IEEEauthorblockN{Juan Juli\'an Merelo Guerv\'os}
\IEEEauthorblockA{Universidad de Granada, CITIC\\
Email: jmerelo@geneura.ugr.es}
}

@@

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight.
\item Non Graph Gamification (G). Only experience is considered
\item Graph Gamification (GG) . Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window.

@@

The three versions of the EvoDrawing web application were deployed to the
Heroku cloud service with the same configuration: using the
Heroku Free option with a 512 MB of RAM, adding only the GrapheneDB and RedisTOGO plug-ins
(the source code is available in GitHub at \url{jcromerohdz/evoDrawing_gaming}).
Table \ref{tab:params} shows the parameters used for the evolutionary algorithm. The graph database 
system used in the implementation was Neo4J as it was already available as a plug-in in Heroku, is well documented
and a scalable solution \cite{miller2013graph,holzschuher2013performance}.

@@

\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure*}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated (X axis) vs. the number of phenotypes evaluated using a logarithmic scale (Y axis). } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}
